\gettitle

### 2019-11-15 assignment2/submission2.tex
Fix solution for 2.1aiii

\section*{1 - Parameter Passing and RMI}
\subsection*{a)}
\begin{enumerate}[label=(\roman*)]
	% no return value, so a is never changed
	\item \texttt{[1, 2, 3, 4, 5]}
	% the code given does not perform a swap, it only overwrites the lower indices with values from the upper ones.
	% because of reference semantics that overwrites the second input as well
	\item \texttt{[5, 4, 3, 4, 5]}
	\item \texttt{[5, 4, 3, 2, 1]} \emph{or} \texttt{[1, 2, 3, 4, 5]} \emph{or} \texttt{[5, 4, 3, 4, 5]}, depending on the exact semantic behaviour of the copy and restore operations.
	Given that the remote server passes the arguments by reference, the first question is whether \textit{x} and \textit{y} have separate copies of \textit{a}. 
	If they do, the first or second option is possible. 
	If there are no separate copies of \textit{a}, the procedure behaves as if the parameters were passed by reference. 
	Otherwise it depends on which value is restored first.
\end{enumerate}

>>>>

\section*{1 - Parameter Passing and RMI}
\subsection*{a)}
\begin{enumerate}[label=(\roman*)]
	% no return value, so a is never changed
	\item \texttt{[1, 2, 3, 4, 5]}
	% the code given does not perform a swap, it only overwrites the lower indices with values from the upper ones.
	% because of reference semantics that overwrites the second input as well
	\item \texttt{[5, 4, 3, 4, 5]}
	\item \texttt{[5, 4, 3, 2, 1]} \emph{or} \texttt{[1, 2, 3, 4, 5]} depending on the order of restore operations.
	The first option appears when \textit{y} is restored before \textit{x}.
	The second option appears when the restoration order is reversed.
\end{enumerate}
